	%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2015--2017}{MSc econometrics}{UvA}{Amsterdam}{\textit{}}{Big data business analytics specialization\\ Focus on machine learning}
\cventry{2012--2014}{BSc econometrics}{UvA}{Amsterdam}{\textit{}}{Minor computational programming}
\cventry{2004--2010}{Bilingual VWO}{'t Atrium}{Amersfoort}{\textit{}}{Including IB English}  % arguments 3 to 6 can be left empty


\section{Master thesis}
\cvitem{title}{\emph{The erroneous use of the Haar wavelet for stock price prediction}}
\cvitem{supervisor}{Prof. Dr. Marcel Worring}
\cvitem{description}{A critical analysis and replication of a well-cited research paper proposing a combination of wavelet transformation and recurrent neural networks for successful stock prediction. Wavelet transformations can be used in time-series analysis to reduce the noise of the signal, or stock prices specifically. Our research criticizes the use of the Haar wavelet by showing that it is both impossible to use in real-time and the sole reason for the reportedly profitable, yet false, 'predictions' shown by Hsieh et al. [2011]. This error was potentially reproduced in more recent research.}

\section{Experience}
\cventry{July 2018-- Aug 2018}{Freelance Python developer}{Ernst \& Young}{Amsterdam}{}{Web development using Django for requesting digital legal documents.
	\begin{itemize}%
		\item Backend web development using the Django web framework built on python and SQLite
		\item Created new frontend web templates using HTML, css and JavaScript
		\item Helped finalize the existing project for the first release
\end{itemize}}

\cventry{June 2017-- June 2018}{Data scientist / Bioinformatician}{TNO: Micro- and Systems biology}{Zeist}{}{Biological data science for research.
	\begin{itemize}%
		\item Standardized statistical analysis with presentable output and interactive reports
		\item Many improvements for research standardization and reproducibility
		\item Shiny applications to make routine tasks accessible to researchers
		\item A great environment to learn from researchers with widespread backgrounds
\end{itemize}}

\cventry{Feb 2015-- Feb 2016}{Excel/VBA application developer}{NZA}{Utrecht}{}{Improving and maintaining processes in Excel and VBA.
	\begin{itemize}%
		\item Automated most routine excel tasks using VBA
		\item Data analysis in R with the saved time
		\item Unique position in the department
\end{itemize}}
\cventry{Nov 2011-- Jul 2015}{Math tutor}{Bijlesnetwerk}{}{}{Teaching mathematics to high school students outside of school.\newline{}}

\cventry{July 2008-- Nov 2013}{Video editor, cameraman}{Stiching POP}{}{}{Filming and editing videos to promote organ music, both for Youtube and DVD. \newline{}}

\cventry{2012--2013}{Content producer}{Qelp}{}{}{Producing manuals for mobile phones using a standardized process.\newline{}}

\section{Languages}
\cvitemwithcomment{Dutch}{Native language}{}
\cvitemwithcomment{English}{High level}{IB diploma}
\cvitemwithcomment{German}{Basic verbal communication}{}

\section{Computer skills}
\cvdoubleitem{Data science}{R, R-Shiny apps and dashboards,\\ Python, Matlab\\}{}{Git, Docker, Galaxy}
\cvdoubleitem{Web}{HTML, CSS, Javascript}{}{Django web framework\\}
\cvdoubleitem{Machine Learning}{Neural Networks, Clustering, SVMs, Decision Trees\\}{}{Evolutionary training algorithms, Feature selection\\}
\cvdoubleitem{Documentation}{RMarkdown, Word, LaTeX\\}{}{}
\cvdoubleitem{Affinity}{Tensorflow, MySQL\\}{}{}

\section{Interests}
\cvitem{Data}{Interactive data visualisation, Game Theory, Computer Science, Bioinformatics, Process Automation}
\cvitem{Free time}{In my free time I play piano, guitar, tabletop/video games and cook food for friends}

\section{Coursera courses 2015/2016}
\cvlistitem{Data Scientist's Toolbox}
\cvlistitem{R Programming (Additional to my study)}
\cvlistitem{Getting and Cleaning Data}
\cvlistitem{Exploratory Data Analysis}
\cvlistitem{Reproducible research}
\cvlistitem{Neural Networks for Machine Learning, by Geoffrey Hinton}
